There's an old saying, "it takes a village to raise a child." A similar statement can be made for a PhD student and their thesis. The first part of the village that must be mentioned is my committee, starting with my advisor, Professor Josh Semeter, who has helped me chase my ideas to fruition and create a piece of my own scholarship. Dr. Phil Erickson at MIT Haystack Observatory has been incredibly helpful and patient in developing this work and without his guidance this would not be possible. Both Professor Hamid Nawab and Professor David Castañón have been very helpful through the great classes they have taught and lending advice on how best to tackle problems.

Before more specific people are detailed I think it needs to be said that Boston University has some incredible institutions within it. The two that have had the most impact on my journey have been the ECE department and the Center for Space Physics. These two institutions have exposed me to a number of different of fascinating ideas and people that I would be hard pressed to find anywhere else.

I have had also a large amount of help from other researchers in the geospace field. This includes Dr. Hanna Dahlgren who was hugely helpful when I was first getting started in the lab. Prof. Matt Zettergren has been extremely helpful in providing simulation data and invaluable advice on other areas.

The are a number of other staff members I would like to thank from MIT Haystack Observatory for all there help. This includes Anthea Coster, Frank Lind, Victor Pankratius, Bill Rideout and Juha Vierinen. 

Staff members from SRI international, have been very helpful as well. This include Mike Nicolls, Steven Chen, Roger Varney and Mary McCready.
 
Accompanying me on my wild ride through academia are my labmates, Nithin, Brent, Michael, Chhavi, Hassan, Sebastian, Greg and Thomas. They have all been excellent collaborators and friends. I also have to add into this mix Matt and Dustin, who although are in a different department, need to be mentioned as if they were part of this group.

There are also many friends beyond just those at BU. Great friends from my days at RPI such Will, Fuzz, Stick, Tristan, Asantha, Steve and Andy have worked hard to stay in touch and hang out whenever possible. Mike, and his wife Kori, helped me get settled at BU after I walked over to his lab unexpectedly to say hi. Dave has been a great friend since I met him at RPI and was a great roommate when I first moved to Boston. I'm also proud to call his wife Meg a great friend, who along with her husband has alway been willing to lend an ear or try to cheer me up if need be using our weird shared sense of humor.

My family members have as always though my life, have been a rock that my foundation is built on. My mother, Sara, has been there since I was born and done her best with the cards that were dealt. My father Herb, who I would like to think would proud of this accomplishment if he were alive today. My sisters Elizabeth and Christine have been incredibly supportive and inspired me to be better by their own actions and through sibling rivalry. My uncle Michael and aunt Maureen have been like a second set of parents to me and their children Matt, Erin and Jimmy have been like a second set of siblings and I'm grateful for everything they've done.

Lastly I want to mention Vanessa, I love you. You (and lets not forget Dexter) make me happier beyond what I thought was possible. Thank you for everything you have given me.



\vskip 1in

\noindent
